Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-11-04 paper/main.tex
revision of discussion until anterior vs. posterior PPA

% Open research question
In this study, we investigate if increased activation in the PPA correlates with
incidental ``spatial information'' in the audio-description of the Hollywood
movie ``Forrest Gump'' (i.e. the audio-only variant of the movie) and, for
cross-modal comparison, in the (actual) audio-visual movie (itself).
% we are different
Since we did not design the given naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews) for optimal localization performance of
the PPA, we operationalize the perception of landscapes and landmarks (compared
to e.g. faces and objects) differently from the reviewed studies.
% operationalization via annotation
Here, we annotated words spoken by the narrator of the audio-description as well
as cuts and depicted locations in the movie.
% public data
We then analyze publicly available data
(\href{http://www.studyforrest.org}{studyforrest.org}) from the same subjects
that listened to the audio-description and watched the movie during fMRI
scanning.
% first: group level AO
First, general linear model (GLM) contrasts based on the audio-description's
annotation are used to test if we could isolate the PPA with an auditory
stimulus on a group level.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to results based on the annotation of the movie.
% individual results
Lastly focussing on the audio-description, we compare results on the level of
individual subjects to results of a block-designed visual localizer experiment
done with the same individuals \citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract and conclusion}
Our results demonstrate that (a), (b), (c).

@@

% all eight AO PPA contrasts
In order to test the robustness of our findings, we created seven additional
$t$-contrasts for the AO stimulus (see Table \ref{tab:ao-contrasts}).
% results
Six of the overall eight AO contrasts show significant bilateral clusters in
anterior regions of the group PPA overlap (see Figure
\ref{fig:stability-slices}.\todo{discuss that contrasts make ``less and less''
sense}
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed contrasts.
% question
\todo[inline]{concluding statement often feels like interpretation/discussion.
Dunno if that is okay.}

% precuneus = retrosplenial cortex ?
\todo[inline]{significant clusters in other regions than PPA could or should (?)
also be reported? Following is a short list:}
% ventral precuneus = retrosplenial cortex?
7 contrasts: bilateral clusters in RSC (and ventral precuneus);
% transverse occipital sulcus = occipital place area
6 contrasts (4 bilat.): transverse occipital sulcus (= OPA?);\todo{check again}
% confounds
4 contrasts: right superior temporal gyrus; 3 contrasts: left superior temporal
gyrus; 3 contrasts: some (smallish) prefrontal clusters

@@

% all eight AV PPA contrasts
Here again in order to test the robustness of our findings, we created four
additional $t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}).
%% results: PPA
All of the overall five AV contrasts yielded significant bilateral clusters (in
that overlap with the PPA group mask/overlap [biggest overlap in posterior part
of group ROI = temporal occipital fusiform cortex] (see Figure
\ref{fig:stability-slices}).
% lingual gyrus
In three contrasts, these homologous clusters extend into the lingual gyri.
% to do
\todo[inline]{check regions again for posterior PPA (cf. text/clusters regarding
group results); border of lingual gyrus belongs to PPA}
% RSC
Further, three contrasts show significant homologous clusters in the RSC.
% LOC
Lastly, four contrasts show significant homologous clusters in lateral occipital
cortices.
% concluding statement
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.
% question
\todo[inline]{concluding statement = interpretation/discussion?}

@@

% AV stimulus
AV stimulus. All contrasts using ``no cut condition'' > x yield null results.
The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
parietal lobe; here again: these kind of nouns and these kind of cuts are
correlated.

@@

% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects.
% results in both subject and group space
Time series of all subjects were analyzed both in group space and subject space.
% report here in group space
For better comparison of results across participants, we here report results
($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).
% individual z-maps -> dataset
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be found
in the accompanying dataset.
% results in detail voxels of significant clusters in PPA ROI (and  RSC
% liberally)
% sub-01 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-02 (m): PPA (l/r), AO (-/-), AV (l/-); RSC: AO (-/-), AV (-/-)
% sub-03 (f): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-04 (f): PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
% sub-05 (m): PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
% sub-06 (m): PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
% sub-09 (m): PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-14 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-15 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-16 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
% sub-17 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-18 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
% sub-19 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-20 (f): PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer \citep{sengupta2016extension} shows ROIs in 12 of 14
subjects and unilateral right clusters in two subjects (sub-04, sub-20).
% subjective threshold
Individual ROIs were assessed by visually inspecting unthresholded $z$-maps, and
setting a subjectively best fitting $z$-threshold to isolate a ROI that matched
the PPA.
% AO
In the current analysis of the AO stimulus, we find significant bilateral
clusters in nine subjects, and one significant cluster in the left hemisphere of
sub-09 that within or overlapping with the PPA ROI.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% AV
For the AV stimulus, results show homologous clusters in five subjects,
unilateral right clusters in sixn subjects (of which one subjects yielded a
unilateral cluster in the dedicated localizer), and a unilateral left cluster in
one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated localizer yielded
only one cluster in the right hemisphere.

\todo[inline]{concluding statements?}

@@

\subsection{Bland-Altman-Plots}

\todo[inline]{anything else to report here? seems more like just an explanation
of the plots}

% why it was done
To better depict the agreement (and difference) between individual results of
the dedicated visual localizer and contrast 1 of the AO paradigm, we created one
Bland-Altman-Plots for each of the 14 subjects (see Figure
\ref{fig:bland-altman}).
% x-axis
The x-axis of every subplot depicts the mean of $z$-values of two spatially
corresponding voxels taken from a subject's unthresholded $z$-map.
% y-axis
The y-axis of every subplot depicts the difference of $z$-values of two
spatially corresponding voxels (dedicated localizer minus AO stimulus).
% masking
We constrained the number of voxels in three ways as indicated by three colors
(grey, blue, red).
% masking in detail
Voxels were spatially constrained to a) voxels located in the occipital and
temporal lobes (gray; using the (probabilistic) Jülich Histological Atlas
\citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
PPA overlap of all subjects (blue), and c) voxels located in the individual PPA
ROI(s)(red).
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AO stimulus.

@@

\todo[inline]{the biggest question: where does the discussion of the stability
of contrasts fit the best?}

\todo[inline]{in general: discussion explains how results fill gap identified in
intro}

\todo[inline]{provides caveats to the interpretation describes how paper
advances the field by providing new opportunities}

@@

% previous studies: visual
On the one hand, previous studies reported bilaterally increased hemodynamic
activity in the PPA when participants were watching static pictures of landscape
compared to face or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal})
% previous study: auditory
On the other hand, a study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% what we did
Hence, we use analogous statistical models in three different experimental
paradigms to compare results gained from a dedicated visual localizer to results
we gained from a movie and the movie's audio-description.
% We focus
Our results suggest that the perception of verbal spatial cues embedded in an
auditory narrative contrasted with non-spatial cues correlate with increased
activation in the PPA of both hemispheres.

@@

\todo[inline]{could maybe pasted into method section to save space here; a short
interpretation is given there already}
% stimuli not designed for research purposes
Both naturalistic stimuli were not designed to be used in a BOLD fMRI experiment
but to entertain their audiences.
% why correlation matrix  was created
Thus, we first tested for correlation of regressors (s. \ref{fig:reg-corr}) that
are based on the annotated stimulus features because a high degree of shared
variance lowers detection power
% results of computing feature correlation
Results show no to minor correlations of regressors across all stimulus
segments.
% encouraged by that we build contrasts (statement)
Thus we felt encouraged to create traditional/canonical voxel-wise GLMs that
modeled and contrasted hemodynamic activity similarly to previous studies that
used simplified stimuli.

@@

\subsection{group level}

\todo[inline]{discuss only PPA here}
% intro
We performed whole-brain analyses on data from the audio-visual movie and its
audio-description. We chose one contrast of each stimulus to be investigated not
just on a group level but also on the level of individual subjects. Additional
contrasts were tested to investigate the stability of results across contrasts
when contrasted categories and the amount of available data is varied.

% AO stimulus cluster location
Group results of the AO stimulus' primary contrast yielded spatially
concise / restricted clusters in the anterior part of the PPA group overlap
taken from \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model hemodynamic responses but modeled from on- to offset of single words
that cue the listener about the movie's missing visual content.
% conclusion
Our group results suggest that auditory spatial information does not just
modulate activity in the PPA (depending on other factors like familiarity; s.
\citep{aziz2008modulation}) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}

% transition to task topic
Moreover unlike most previous studies, our paradigm was free of any task.
%
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Our paradigm still differs from previous studies because the relevant stimulus
features were incidentally embedded in a continuous auditory stream.
% conclusion
This embeddedness prevents participants from making assumptions about the
investigated perceptual process by just being exposed to the paradigm and thus
mimics experiencing the world outside the lab more closely.
% concluding statement: kinda automatic process
The lack of a task further suggests verbal spatial information is processed in
the PPA in an automatic fashion and does not necessarily rely on deliberately
paying attention to spatial information.

\paragraph{shortcomings of AO contrasts}

\todo[inline]{cf. Methods: annotation \& Methods: AO copes}
% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal cues regarding
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room/locale (\texttt{groom}) to
non-spatial cues.
% we did not choose se\_new and se\_old
Notably, we did not choose the categories that contained switches from one
setting to another (texttt{se\_new} and texttt{se\_old}) which one might assume
to contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
These categories were actually heterogeneous: they rarely contained whole (and
thus vague) descriptions of landscapes (e.g. ``in a football stadium'',
``Forrest is running through the jungle'') but mostly landmarks or buildings,
and also non-spatial cues.\todo{repeat examples from method section}.
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of wholistic but vague verbal descriptions of
landscapes correlate with differential hemodynamic activity in the PPA compared
to more concrete spatial cues.

\subsubsection{AV stimulus}
% location
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPAs from anterior to posterior and
expand into retrosplenial regions.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex)\todo{which of these regions overlap
with group ROI? which regions show clusters but do not overlap with PPA?}
% confound of higher perception
This can be attributed to the fact that we averaged the content of individual
frames after a cut and did not control for confounding features like depicted
faces or objects.
% confounds of lower perception
It further suggest low-level visual features were not averaged out leading to
clusters spanning the intracalcarine cortex.
% further studies
Since the capability to isolate clusters or networks correlating with specific
perceptual (or cognitive) processes is influenced by the amount of annotated
stimulus features further studies focusing on visual perception should annotate
and model visual features of naturalistic stimuli more rigorously.\todo{ouf,
okay...}
% cross-modal control purpose?
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
results?}

@@

\todo[inline]{the pain starts exactly here}

% why we did a couple of contrasts
For both stimuli we created additional contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.

\subsubsection{PPA}
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show
significant bilateral clusters in the anterior part of the group PPA.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but extending into posterior regions
% no incidental findings
Results of the additional contrasts suggest that bilaterally increased
activation in the PPA does not depend on accidental findings but is are stable
across contrasts of the movie and the audio-description.

% but
Results also suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% what's going on
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo[inline]{god forgive me for this paragraph}
% null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements, or
memory.\todo{which kind of memory}

% BUT: amount of data
Nevertheless, localization performance is influenced by the amount of available
data\todo{give examples of contrast using less events in AV and AO} and how well
events within categories matched on average the preferred stimulus type.
% example AV: data amount and category homogeneity
For example in the AV stimulus, we averaged different kind of movie cuts
regardless to the movie frames content.\todo[inline]{how well spatially
constrained are the clusters?}
% results
As a result, clusters are more widespread and reach into early visual cortex.

\todo[inline]{first: number of available events -> ``noise''}

\todo[inline]{second: category match -> ``localization performance''}

% AO: stimulus categories
For example in the AO stimulus, nouns of the narrator that cue a switch to
another setting belong to different categories (s. above).\todo[inline]{Number
of events in which contrasts?}
% example for data amount AO: superior temporal cortex
In four of nine contrasts of the AO stimulus, we find significant clusters in
superior auditory cortices (including early auditory cortices?)\todo{which
exactly}
% conclusion
This suggests that variance correlating with lower level auditory processes was
(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
nuisance regressors?}
% foreshadowing of narrator by soundscape
Further, verbal cues are regularly forestalled by changes of the
soundscape.\todo{cross-modal control contrasts; all negative results at moment
of cuts but vse\_new > pe\_old): right RSC.}
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.
% conclusion: AO and AV stability
In summary, our results across add further evidence that model-driven analyses
can be run on data from naturalistic stimuli to isolate brain activity
correlating with specific perceptual processes.
% but
Nevertheless isolation performance relies on how well the model captures
different aspects of the stimuli's feature space.

\subsubsection{other systematics: anterior vs. posterior, RSC and OPA}

% intro
Nevertheless, results across contrasts of both stimuli show significant clusters
constrained to the anterior part of the PPA in contrasts of the AO stimulus, and
significant clusters in the retrosplenial cortices and superior lateral cortices
in both naturalistic stimuli.

\subsection{anterior vs posterior PPA: contextual associations}

>>>>

% Open research question
In this study, we investigate if increased activation in the PPA correlates with
incidental ``spatial information'' in the audio-description of the Hollywood
movie ``Forrest Gump'' (i.e. the audio-only variant of the movie) and, for
cross-modal comparison, in the (actual) audio-visual movie (itself).
% we are different
Since we did not design the given naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews) for optimal localization performance of
the PPA, we operationalize the perception of landscapes and landmarks (compared
to e.g. faces and objects) differently from the reviewed studies.
% operationalization via annotation
Here, we annotated words spoken by the narrator of the audio-description as well
as cuts and depicted locations in the movie.
% public data
We then analyze publicly available data
(\href{http://www.studyforrest.org}{studyforrest.org}) from the same subjects
that listened to the audio-description and watched the movie during fMRI
scanning.
% first: group level AO
First, general linear model (GLM) contrasts based on the audio-description's
annotation are used to test if we could isolate the PPA with an auditory
stimulus on a group level.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to results based on the annotation of the movie.
% individual results
Lastly focussing on the audio-description, we compare results on the level of
individual subjects to results of a block-designed visual localizer experiment
done with the same individuals \citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract, intro to
discussion and conclusion}
Our results demonstrate that (a), (b), (c).

@@

% all eight AO PPA contrasts
In order to test the robustness of our findings, we created seven additional
$t$-contrasts for the AO stimulus (see Table \ref{tab:ao-contrasts}).
% results
Six of the overall eight AO contrasts show significant bilateral clusters in
anterior regions of the group PPA overlap (see Figure
\ref{fig:stability-slices}.\todo{Discussion: discuss that contrasts make ``less
and less'' sense}
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed contrasts.
% question
\todo[inline]{concluding statement often feels like interpretation/discussion}

% precuneus = retrosplenial cortex ?
\todo[inline]{significant clusters in other regions than PPA could or should (?)
also be reported? Following is a short list:}
% ventral precuneus = retrosplenial cortex?
7 contrasts: bilateral clusters in RSC (and ventral precuneus);
% transverse occipital sulcus = occipital place area
6 contrasts (4 bilat.): transverse occipital sulcus (= OPA?);\todo{AO: clusters
are more lateral; AV: clusters are more medial}
% confounds
4 contrasts: right superior temporal gyrus; 3 contrasts: left superior temporal
gyrus; 3 contrasts: some (smallish) prefrontal clusters

@@

% all eight AV PPA contrasts
Here again in order to test the robustness of our findings, we created four
additional $t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}).
%% results: PPA
All of the overall five AV contrasts yielded significant bilateral clusters (in
that overlap with the PPA group mask/overlap [biggest overlap in posterior part
of group ROI = temporal occipital fusiform cortex] (see Figure
\ref{fig:stability-slices}).
% lingual gyrus
In three contrasts, these homologous clusters extend into the lingual gyri.
% RSC
Further, three contrasts show significant homologous clusters in the RSC.
% LOC
Lastly, four contrasts show significant homologous clusters in lateral occipital
cortices.
% concluding statement
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.
% question
\todo[inline]{concluding statement = interpretation/discussion?}

@@

% AV stimulus
AV stimulus. All contrasts using ``no cut condition'' > x yield null results.
The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
parietal lobe; here again: these kind of nouns and these kind of cuts are
correlated (cf. Figure \ref{fig:reg-corr}).

@@

% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects.
% results in both subject and group space
Time series of all subjects were analyzed both in group space and subject space.
% individual z-maps -> dataset
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05 cluster
corrected) can be found in the accompanying dataset.
% report here in group space
For better comparison of results across participants, we here report results
($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (transversal slice z=-11 for all subjects).

% results in detail voxels of significant clusters in PPA ROI (and  RSC
% liberally)
% sub-01 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-02 (m): PPA (l/r), AO (-/-), AV (l/-); RSC: AO (-/-), AV (-/-)
% sub-03 (f): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-04 (f): PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
% sub-05 (m): PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
% sub-06 (m): PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
% sub-09 (m): PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-14 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-15 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-16 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
% sub-17 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-18 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
% sub-19 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-20 (f): PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
12 of 14 subjects and a unilateral right clusters in two subjects (sub-04,
sub-20).
% procedure in Sengupta
Individual ROIs were assessed by visually inspecting unthresholded $z$-maps of
three different contrasts, and setting a subjectively best fitting $z$-threshold
to isolate a ROI that matched the PPA.
% AO
In the current analysis of the AO stimulus, we use the same AO (and AV) contrast
for all subjects. We find statistically significant bilateral clusters in nine
subjects, and one cluster in the left hemisphere of sub-09 that are within or
overlapping with the PPA ROI.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% AV
Results of the AV contrast yield homologous clusters in five subjects,
unilateral right clusters in six subjects (of which one subjects yielded a
unilateral cluster in the dedicated localizer), and a unilateral left cluster in
one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated localizer yielded
only one cluster in the right hemisphere.
% concluding statement
\todo[inline]{concluding statement that does not sound like
interpretation/discussion?}

@@

\todo[inline]{anything else to report in the following paragraph? seems more
like just an explanation of the plots}
% Bland-Altman-Plots: why they were done
To better depict/convey the agreement and difference between individual results
of the dedicated visual localizer and the primary AO contrast, we created one
Bland-Altman-Plots for each of the 14 subjects (see Figure
\ref{fig:bland-altman}).
% x-axis
The x-axis of every subplot depicts the mean of $z$-values of two spatially
corresponding voxels taken from a subject's unthresholded $z$-map.
% y-axis
The y-axis of every subplot depicts the difference of $z$-values of two
spatially corresponding voxels (dedicated localizer minus AO stimulus).
% masking
Voxels were spatially constrained to a) voxels located in the occipital and
temporal lobes (gray; using the probabilistic Jülich Histological Atlas
\citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
PPA overlap of all subjects (blue), and c) voxels located in the individual PPA
ROI(s)(red).
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AO stimulus.

@@

\todo[inline]{the structure is as follows at the moment: correlation of
regressors; AO group; AV group; robustness AO + AV; anterior vs posterior PPA;
other clusters significant across contrasts (= retrosplenial cortex and
occipital place area)}

\todo[inline]{discussion explains how results fill gap identified in
intro}

\todo[inline]{provides caveats to the interpretation describes how the paper
advances the field by providing new opportunities}

@@

% previous studies: visual
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to face or
objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal}) whereas one
study using spoken sentences reported mixed results \citep{aziz2008modulation}.
% we use similar statistical models but with naturalistic stimuli
Here, we use statistical models that are similar to previous studies that used
small sets of experimentally controlled stimuli to investigate hemodynamic brain
responses during two naturalistic stimuli.
% more than just one contrast
We computed varying GLM contrasts that differed in the contrasted categories and
the amount of available data to test the robustness of our findings in both
stimuli.
% comparison to localizer experiment
We compare results of the primary contrast of each stimulus on the level of
individual subjects to results that we gained from a dedicated visual localizer
paradigm done with the same subjects \citep{sengupta2016extension}.
% summary of results main finding
Results of our whole-brain analyses suggest that the perception of verbal
``spatial information'' embedded in an auditory narrative contrasted with
``non-spatial information'' correlate with increased activation in the PPA of
both hemispheres.
% to do
\todo[inline]{this is just the main finding; other possible ``honourable''
mentions like robustness of results, AV stimulus, individual results?}

@@

\todo[inline]{Following paragraph could pasted into method section to save space
here; a short interpretation is given there already; so methods/ results/
discussion are not absolutely separated there already}
% stimuli not designed for research purposes
Both naturalistic stimuli were not designed to be used in a BOLD fMRI experiment
but to entertain their audiences.
% why correlation matrix  was created
Thus, we first tested for correlation of regressors (s. \ref{fig:reg-corr}) that
are based on the annotated stimulus features because a high degree of shared
variance lowers detection power
% results of computing feature correlation
Results show no to minor correlations of regressors across all stimulus
segments.
% encouraged by that we build contrasts (statement)
Thus we felt encouraged to create traditional/canonical voxel-wise GLMs that
modeled and contrasted hemodynamic activity similarly to previous studies that
used simplified stimuli.

@@

\subsection{group level: AO \& AV (PPA only)}

% AO stimulus
Group results of the AO stimulus' primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap taken from
\citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model hemodynamic responses but modeled from on- to offset of single words that
cue the listener about the movie's missing visual content.
% conclusion
Our group results suggest that auditory spatial information does not just
modulate activity in the PPA (depending on other factors like familiarity; s.
\citep{aziz2008modulation}) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}

% Previous studies used tasks
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but epstein1998
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Our paradigm still differs from previous studies because the relevant stimulus
features were incidentally embedded in a continuous stream of auditory
information.
% conclusion
This embeddedness prevents participants from making assumptions about the
investigated perceptual process by just being exposed to the paradigm and thus
mimics experiencing the world outside the lab more closely.
% concluding statement: kinda automatic process
The lack of a task further suggests verbal spatial information is processed in
the PPA in an automatic fashion and does not necessarily rely on deliberately
paying attention to spatial information.

\todo[inline]{following: how to frame it (better) that AV merely serves as
conceptual control?; imo should be a small section anyway}
% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPAs from anterior to posterior and
expand into retrosplenial regions.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
overlap) with group ROI?}
% confound of higher perception
This can be attributed to the fact that we averaged the content of individual
frames after a cut and did not control for confounding features like depicted
faces or objects.
% confounds of lower perception
It further suggest low-level visual features were not averaged out leading to
clusters spanning the intracalcarine cortex.
% cross-modal control purpose?
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
results?}

@@

% why we did a couple of contrasts
For both stimuli we created additional contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but extending into posterior regions.
% results indicate robustness
Results of the additional contrasts indicate that our findings are robust across
contrasts and do not depend on the design of one specific contrasts.

% but
Nevertheless, results also suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AO stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA ROI.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements(, or
memory).\todo{which kind of memory}
% AO: auditory cortices
For example in the AO results, contrasts that compare (among other categories)
verbal cues about the change of a setting (\texttt{se\_new} > \texttt{se\_old})
to categories that do not cue a change of a setting (contrasts 2, 3, 6, 7) show
significant clusters in (primary and secondary) auditory cortices.\todo{``poor
job of nuisance regressors?}
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not do their fucking
job (it is still kinda innate in the contrast).
% possible reason
This could be attributed to a possible change of the soundscape and/or increased
volume when the narrative switches to a new setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

\subsection{consistencies across contrasts}

\subsubsection{anterior vs. posterior PPA}

% intro
Notably, results of the AO contrasts consistently yielded significant clusters
spatially constrained to the anterior part of the PPA group overlap (and
anterior part of significant clusters of the AV contrasts).

\todo[inline]{following are quotes from references for brainstorming what might
theoretically make sense}

% connectivity
\citep{aminoff2013role} regarding \citep{baldassano2013differential}: a
neuroimaging study examining functional connectivity of differences between
anterior and posterior regions of the PHC show that anterior regions are more
functionally connected to retrosplenial complex (RSC) and parietal cortices,
whereas the posterior regions are more functionally connected to visual
processing regions.
